First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
added the suggestions from Stepan

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
radial time projection chamber (RTPC) was used to detect the recoiling $^4$He 
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries (BSA) are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, chiral even Generalized Parton 
Distribution (GPD) H of $^4$He.

We measured beam spin asymmetries significantly larger than that observed on 
proton targets and extracted, in a completely model independent way, the chiral 
even generalized parton distribution (GPD) of the $^4$He nucleus. This 
pioneering measurement leads the way toward the 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

A wealth of information on quantum chromodynamics (QCD) lies in the 
internal structure of hadrons. In the recent past, development of the 
generalized parton distributions (GPDs) framework has offered the possibility
to obtain new information about the momentum and spatial degrees of 
freedom of the quark and gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of
DVCS is considered the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements focused on the study of 
proton structure and allowed extraction of the tomography of the nucleon (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

The coherent nuclear DVCS channel, $eA \rightarrow e' A' \gamma$, is 
difficult to measure due to its small cross section and the necessity to 
ensure the target remains intact while emitting a hard photon.  Figure 
\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on $^4$He.  
Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
interaction and is calculable with perturbative QED.  The non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
transferred to the target, however $x$ cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) \cite{Guidal:2013rya} defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

The main challenge in studying nuclear DVCS is ensuring the exclusivity of 
the reaction. Until now, the only available data set of nuclear DVCS
was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was 
based only on kinematic cuts on the measured scattered electron and real photon. 
That measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
Xe), but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, so we 
built a dedicated radial time projection chamber (RTPC) for the detection of 
the recoiling low energy nuclei in order to complete this experimental setting.  
The $^4$He nucleus is an ideal experimental target in this regard, as it is 
light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density.  A helium target leads to another important advantage, as the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. This significantly
simplifies the interpretation of the data and allows a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
end of this letter.

@@

The experiment E08-024 took place in Hall-B at JLab
in 2009 using the nearly 100\% duty factor, longitudinally 
polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
target placed in the center of CLAS. For DVCS experiments, the CLAS baseline 
design \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and 
a solenoid. The IC extends the photon detection acceptance of CLAS, which was 
originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angles as low as 
4$^{\circ}$. At these small angles the low-energy M\o{}ller electrons produced 
in the target form a very high rate background that is
suppressed by a 5 Tesla solenoid placed around the target.

Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
$^4$He nuclei produced in DVCS have a low average momentum around 300 
MeV/c. CLAS cannot detect such low energy $\alpha$ particles, 
so in order to ensure the exclusivity of the measurement, we built a small and 
light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents the design of 
this RTPC and the $^4$He gaseous target in its center. The detector was 
calibrated specifically for the detection of
$^4$He nuclei based on elastic scattering with a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one 
electron, one $^4$He, and at least one photon are detected in the final state. 
Electrons are identified by using fiducial cuts and requiring appropriate
signals in all the sub-detectors of the baseline CLAS (drift chambers, 
Cherenkov counters, electromagnetic calorimeter, and time of flight 
scintillators). The $^4$He tracks are identified with fiducial, 
timing and track quality cuts in the RTPC detector. In addition,
we apply a vertex matching cut to ensure the electron and helium
nucleus originate from the same position. The photons are detected in either
the IC or the CLAS electromagnetic calorimeter.  Note that even though the 
DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. This is 
motivated by the fact that, while soft photons are likely to be produced in random 
coincidence, they cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
The most energetic photon is always considered as the DVCS photon candidate.

@@

To ensure the interaction 
occurs at the partonic level and the DVCS handbag diagram is dominant, we 
select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is 
optimized by applying a set of cuts on the following kinematic variables: the 
co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
squared, the missing transverse momentum, the missing mass squared of the 
$e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the 
missing energy (which appears to be too large and for which we reduced the cut 
window to [-0.45,0.5] GeV).  We also reject events where a $\pi^0$ is identified
by invariant mass reconstruction of two photons.  After these requirements, we have
about 3200 events left, and Figure \ref{fig:kin-coverage} presents their kinematic
distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

We identified two main backgrounds to our measurement, accidental 
coincidences and exclusive, coherent $\pi^0$ production. The accidentals have 
particles originating from different events, and we estimate their  contribution
to be 4.1\% of our sample. We evaluated this contribution by selecting events 
passing all our cuts but with an electron and helium originating from different 
vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
one of the two photons from the $\pi^0$ decay is produced at low energy in the 
laboratory frame and remains undetected. To estimate the importance of this 
background, we developed an event generator calibrated on the experimental yield 
of exclusive $\pi^0$ measured by our experiment. We used this generator together 
with a GEANT3 simulation of our detection system to estimate the ratio between
the number of $\pi^0$ events where the two photons are detected and those that 
would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
of exclusive $\pi^0$ events to correct the DVCS data. Depending on the kinematics, we
found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
errors sum up to about 10\%, which always remain significantly smaller than the 
statistical errors.

%asymmetries
Several observables related to DVCS are of interest, but in this work we focus only 
on the beam-spin asymmetry. This  observable is measurable using a polarized 
lepton beam on an unpolarized target (U). It is convenient to use the beam-spin 
asymmetry because most of the experimental normalization and acceptance issues 
cancel out in the asymmetry ratio. It is defined in terms of the cross sections 
as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
can be expressed in terms of the measured number of events in each 
beam-helicity state ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of DVCS events detected with positive and negative electron helicity with 
respect to the beam direction.

@@

Due to limited statistics, we only bin  our data two-dimensionally 
 in the azimuthal angle ($\phi$) and one of the kinemtical variables 
$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents $A_{LU}$ for the three
sets of binning. The asymmetries are fitted with the form of
equation \ref{eq:A_LU-coh}, where the real and imaginary part of the CFF
$\mathcal{H}_{A}$ are the free parameters of the fit. Figure \ref{fig:alu90} 
shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model relies on the impulse approximation and uses 
advanced spectral functions of nuclei. The calculations are at slightly different 
kinematics than our data but still provide some guidance. The experimental 
results appear to have larger asymmetries than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions.

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
radial time projection chamber (RTPC) was used to detect the recoiling $^4$He 
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries (BSA) are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the chiral even Generalized 
Parton Distribution (GPD) $H_{A}$ of $^4$He. This pioneering measurement leads 
the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on Quantum Chromodynamics (QCD) lies in the internal structure 
of hadrons. In the recent past, development of the Generalized Parton 
Distributions (GPDs) framework has offered a possibility to obtain new 
information about the momentum and spatial degrees of freedom of the quark and 
gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of deep virtual Compton scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed extraction of the tomography of the nucleon (for details 
on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
to measure due to its small cross section and the necessity to ensure 
exclusivity of the reaction, i.e. the target nucleus. Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure Compton Form
Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:

\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

The main challenge in studying nuclear DVCS is ensuring the exclusivity of the 
reaction. Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was based only on 
kinematic cuts on the measured scattered electron and real photon.  That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, so we 
built a specialized radial time projection chamber (RTPC) for detection of a 
low energy recoiling light nuclei in order to ensure exclusivity of the 
reaction. The $^4$He nucleus is an ideal experimental target in this regard, as 
it is light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density.  A helium target leads to another important advantage, as the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. This significantly
simplifies the interpretation of the data and allows a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
end of this letter.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed in the center of CLAS. For DVCS 
experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
low-energy M\o{}ller electrons produced in the target form a very high rate 
background that is suppressed by a 5 Tesla solenoid placed around the target.

In our kinematics, the recoil 4He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
RTPC installed in the experimental hall, and the rendering showing detector 
components and the $^4$He detection concept are presented. The $^4$He gaseous 
target, a $25$ cm long, $27~\mu$m wall Kapton straw, in the center was part of 
the RTPC assembly. The detector was calibrated specifically for the detection 
of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one 
electron, one $^4$He, and at least one photon are detected in the final state.
Electrons are identified using measured momentum, time and energy in fiducial 
volume of CLAS drift chambers, Cerenkov counters, scintillator counters, and 
electromagnetic calorimeters. The $^4$He are identified in the RTPC using time, 
track quality, and energy loss cut for tracks in the fiducial region. In 
addition, we apply a vertex matching cut to ensure that the electron and helium
nucleus originate from the same position. The photons are detected in either
the IC or the CLAS electromagnetic calorimeter. Note that even though the DVCS 
reaction has only one real photon in the final state, events with more than one 
good photon are not discarded at this stage. This is motivated by the fact 
that, while soft photons are likely to be produced in random coincidence, they 
cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
The most energetic photon is always considered as the DVCS photon candidate.

@@

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$.  
Exclusivity of the coherent DVCS reaction is optimized by applying a set of 
cuts on the following kinematic variables: the co-planarity angle ($\Delta 
\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) and 
($\gamma^*,^4He'$) planes, the missing energy, the missing mass squared, the 
missing transverse momentum of the $e'^4He'\gamma$ system, the missing mass 
squared of the $e'^4He'$ system, and the angle ($\theta$) between the measured 
photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
these cuts are presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ 
cuts except for the missing energy (which appears to be too large and for which 
we reduced the cut window to [-0.45,0.5] GeV).  We also reject events where a 
$\pi^0$ is identified by invariant mass reconstruction of two photons.  After 
these requirements, we have about 3200 DVCS events left, and Figure 
\ref{fig:kin-coverage} presents their kinematic distributions in 
($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the Beam Spin Asymmetry (BSA). The BSA on unpolarized target (U), $A_{LU}$, is 
measurable by the difference of cross sections of the reaction at opposite beam 
helicities normalized to the total cross section. It is written as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
can be expressed in terms of the measured number of events in each 
beam-helicity state ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of DVCS events detected with positive and negative electron helicity with 
respect to the beam direction. In this ratio most of uncertainties of the 
experimental normalization and in detector efficiencies will cancel out.

@@

Due to limited statistics, we only bin  our data two-dimensionally 
 in the azimuthal angle ($\phi$) and one of the kinemtical variables 
$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents $A_{LU}$ for the three
sets of binning. The asymmetries are fitted with the form of
equation \ref{eq:A_LU-coh}, where the real and imaginary part of the CFF
$\mathcal{H}_{A}$ are the free parameters of the fit. We identified two main 
backgrounds to our measurement, accidental coincidences and exclusive, coherent 
$\pi^0$ production. The accidentals have particles originating from different 
events, and we estimate their  contribution to be 4.1\% of our sample. We 
evaluated this contribution by selecting events passing all our cuts but with 
an electron and helium originating from different vertices. Regarding the 
$\pi^0$ production, it can easily be mistaken for DVCS when one of the two 
photons from the $\pi^0$ decay is produced at low energy in the laboratory 
frame and remains undetected. To estimate the importance of this background, we 
developed an event generator calibrated on the experimental yield of exclusive 
$\pi^0$ measured by our experiment. We used this generator together with a 
GEANT3 simulation of our detector to estimate the ratio between the number of 
$\pi^0$ events where the two photons are detected and those that is 
misidentified as DVCS events. This ratio is then multiplied by the measured 
yield of exclusive $\pi^0$ events to correct the DVCS data. Depending on the 
kinematics, we found contaminations of 2 to 4\%. The study of systematics 
uncertainties showed that the main contributions come from the choice of the 
DVCS exclusivity cuts (8\%) and the large binning size (5.1\%). However, added 
quadratically,the total systematic uncertainty is about 10\%, which is 
significantly smaller than statistical uncertainties in all kinematical bins. 
Figure \ref{fig:alu90} shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
fitted $A_{LU}$ signals at $\phi$~=~90$^{\circ}$. The $x_{B}$ and 
$-t$-dependencies are compared to theoretical calculations performed by 
S.~Liuti and K.~Taneja \cite{simonetta_2}. Their model relies on the impulse 
approximation and uses advanced spectral functions of nuclei. The calculations 
are at slightly different kinematics than our data but still provide some 
guidance. The experimental results appear to have larger asymmetries than the 
calculations. These differences may arise from nuclear effects which are not 
taken into account in the model, such as long-range interactions.
